The Impact of Alternation

### 2017-05-13 draft.tex
ok

The main idea behind the above definition of the interpolation problem
is that we would like to obtain an interpolant $\tuple{\top,I_0(Q),
  I_2(Q,\vec{x}), \ldots, I_{n}(Q,\vec{x}),\bot}$ whose formulae
\emph{combine states with the data constraints that must hold
  locally}, whenever the control reaches a certain boolean
configuration. This association of states with data valuations is
tantamount to defining efficient semi-algorithms, based on lazy
abstraction \cite{HJMS02}. Furthermore, the abstraction defined by the
interpolants generated in this way can also \emph{over-approximate the
  control structure} of an automaton, in addition to the sets of data
values encountered throughout its runs.

@@

  To prove the first point, assume that $L(\A) \neq \emptyset$. By the
  previous point, Algorithm \ref{alg:impact} does not return
  $\true$. Suppose, by contradiction, that it does not terminate and
  conclude using the breadth-first exploration argument from the proof
  of Theorem \ref{thm:predabs}. \qed}

>>>>

The main idea behind the above definition of the interpolation problem
is that we would like to obtain an interpolant $\tuple{\top,I_0(Q),
  I_1(Q,\vec{x}), \ldots, I_{n}(Q,\vec{x}),\bot}$ whose formulae
\emph{combine states with the data constraints that must hold
  locally}, whenever the control reaches a certain boolean
configuration. This association of states with data valuations is
tantamount to defining efficient semi-algorithms, based on lazy
abstraction \cite{HJMS02}. Furthermore, the abstraction defined by the
interpolants generated in this way can also \emph{over-approximate the
  control structure} of an automaton, in addition to the sets of data
values encountered throughout its runs.

@@

  To prove the first point, assume that $L(\A) \neq \emptyset$. By the
  previous point, Algorithm \ref{alg:impact} does not return
  $\true$. Suppose, by contradiction, that it does not terminate and
  conclude using the breadth-first argument from the proof of Theorem
  \ref{thm:predabs}. \qed}
